---
title: "p8105_hw1_AG2965"
output: github_document
---

We will load the penguins dataset.
```{r}
data("penguins", package = "palmerpenguins")
```

We will load the tidyverse. 
```{r}
library(tidyverse)
```
# Problem 1
## Description of the penguins dataset
### Data in this dataset:

The penguins dataset has 8 variables, including 'species', 'island', 'bill_length_mm', 'bill_depth_mm', 'flipper_length_mm', 'body_mass_g', 'sex', and 'year'. There 3 species of penguins on 3 islands included.

### Size of the dataset:
There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in this dataset. 

### Mean flipper length:
```{r}
prob_1_df=penguins
```

The mean flipper length is `r mean(pull(prob_1_df,flipper_length_mm), na.rm = TRUE)`

### Scatterplot

```{r chunk_scatterplot, echo=FALSE}
ggplot(penguins, aes(x=bill_length_mm,y=flipper_length_mm, color=species)) + geom_point()
```

We will save the scatterplot as a PDF file. 
```{r}
ggsave("p8105_hw1_AG2965.pdf", height=7, width=5)
```

# Problem 2
This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

Create a data frame comprised of:

1) a random sample of size 10 from a standard Normal distribution
2) a logical vector indicating whether elements of the sample are greater than 0
3) a character vector of length 10
4) a factor vector of length 10, with 3 different factor “levels”
