---
title: "p8105_hw1_AG2965"
output: github_document
---

We will load the penguins dataset.
```{r}
data("penguins", package = "palmerpenguins")
```

We will load the tidyverse. 
```{r}
library(tidyverse)
```

# Problem 1
## Description of the penguins dataset
### Data in this dataset:

The penguins dataset has 8 variables, including 'species', 'island', 'bill_length_mm', 'bill_depth_mm', 'flipper_length_mm', 'body_mass_g', 'sex', and 'year'. There 3 species of penguins on 3 islands included.

### Size of the dataset:
There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in this dataset. 

### Mean flipper length:
The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`

### Scatterplot

```{r chunk_scatterplot, echo=FALSE}
ggplot(penguins, aes(x=bill_length_mm,y=flipper_length_mm, color=species)) + geom_point()
```

We will save the scatterplot as a PDF file. 
```
ggsave("p8105_hw1_AG2965.pdf", height=7, width=5)
```


# Problem 2
This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

Create a data frame comprised of:

1) a random sample of size 10 from a standard Normal distribution
2) a logical vector indicating whether elements of the sample are greater than 0
3) a character vector of length 10
4) a factor vector of length 10, with 3 different factor “levels”

```{r}
df=tibble(randomsample=rnorm(10),
               vec_logic = randomsample > 0,
               vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j" ),
               vec_factor = factor(c("small", "small", "small", "medium", "medium", "medium", "large", "large", "large", "large")))
```

#Mean of random sample of size 10 from a standard normal distribution, this works
The mean `r mean(pull(df, randomsample))`

#Mean of a logical vector indicating whether elements of the sample are greater than 0, this works
The mean `r mean(pull(df, vec_logic))`

#Mean of a character vector of length 10, this doesn't work
The mean `r mean(pull(df, vec_char))`

#Mean of a factor vector of length 10, with 3 different factor “levels”
The mean `r mean(pull(df, vec_factor))`
 
#We can also use R to convert variables from one type to another. In this case, we will convert the logical, character, and factor vectors into a numeric variable using the as.numeric function. We find that the logical vector (vec_logic) and the factor vector (vec_factor) become numeric, but the character vector (vec_charac) cannot. This means that we cannot perform descriptive statistics, such as taking the mean, on the character vector, but we can do so on the logical vector and the factor vector. This may be because the character vector has only distinct characters that make the conversion to numeric characters difficult.

```{r eval = FALSE}
as.numeric(df$vec_logic)
as.numeric(df$vec_char)
as.numeric(df$vec_factor)
```
  )